%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary and conclusion}
\label{sec:conclusion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\add{For the case of disk galaxies}, we have studied both the RCs and \add{different galaxy scaling relations (such as the Radial Acceleration Relation, MDAR, DM surface density Relation and the Ferrarese Relation connecting the total halo mass and its supermassive central object)} within the SPARC data-set, from an alternative perspective in which the halos are formed through a MEP. 
\add{Within this paradigm,} we considered the DM halo as a self-gravitating system of neutral fermions at finite temperature, while the baryonic mass components were provided from the SPARC data-set. 
%We faced the intricate relation between the mass distribution of dark and baryonic matter for disk galaxies from a different perspective compared to the cosmological $\Lambda$CDM principles and MOND. Thus, we considered dark matter as a self-gravitating system composed of elementary fermions while the baryonic component was provided from the SPARC data base.

For comparison, we have also considered the DC14 (\add{or generalized NFW}) model which contains different physics such as the influence of baryonic feedback in the morphology of CDM halos. In addition, we have taken into account empirical DM fitting models motivated \add{either} from DM-only simulations like NFW \add{(within CDM}), and Burkert \add{(within WDM); or the Einasto model as recently studied in \citet{2019MNRAS.483.4086B} accounting for baryonic effects (through hydrodynamical zoom-in simulations) in either cosmology}. Finally their best-fits to the acceleration relations and SPARC RCs were compared with the fermionic model \add{in sections \ref{sec:result:ac} and \ref{sec:result:gof} respectively}. %to try to gain some physical insights to the nature of the DM and its impact on the inner halo morphology.

For all competing DM models, we fitted the DM contribution to the RC as inferred from the given total rotation curve and the baryonic components. An alternative fitting approach is minimizing the least square errors of the total rotation curve (e.g. $V_i = V_{i, \rm tot}$) where the predictions are a composition of a theoretical DM halo model and the baryonic component inferred from observation. On theoretical ground, such an approach is not identical to the approach explained in section \ref{sec:fitting} since the propagation of uncertainty produces a somewhat different weighting. However, we have repeated the same analysis on both approaches and obtained consistent results despite few minor numerical variations, and without changing any qualitative conclusion obtained in this work.

The main results obtained in this paper can be summarized as follows, according to three different issues:
\begin{description}
\item[Acceleration relations] The Radial Acceleration Relation as well as the MDAR relation analyzed here are based on an averaging of many spiral galaxies and holds for different Hubble types. Our analysis shows that all competing DM models are able to reproduce those relations, although without a clear favourite because all are similarly good (see \cref{fig:acceleration:grid}). For instance, for all DM models, we obtain nearly identical values for $\SYMafrak$ as required in \cref{eq:mcgaugh-fit}. This result is in line with a recent analysis done in \citet{2020JCAP...06..027K}. 

\item[Individual RC fitting] A deeper understanding of the Radial Acceleration Relation \add{and MDAR} is backed by a goodness of model analysis for $120$ filtered and individual galaxies of the SPARC data set covering different Hubble types. The DM contribution to the RCs reflect some diversity in galaxies which, in general, are better fitted by cored DM halo models instead of cuspy (e.g. NFW). This is not only in agreement with a similar analysis done by \citet{2020ApJS..247...31L}, but totally in line with the results of \citet{2020JCAP...06..027K}. That is, it has been shown here that the DM halo models suitable to explain the acceleration relations do not necessary explain well the SPARC RCs.

Comparing the fitting goodness of DC14 and NFW implies that baryonic feedback mechanism is important in galaxy formation. On the other hand, comparing the fermionic model with DC14 \add{or Einasto} yields an interesting hint regarding baryonic-to-dark relations: we found that the fermionic model is equally good in fitting galaxies which require a significant escape of particles (i.e. $W_p < 10$) (\add{see \ref{sec:result:gof} and bottom pnnel in \cref{fig:goodness:with-cutoff}}). This may imply that for those galaxies baryonic feedback is \add{less relevant, thus} hinting on the importance of a quasi-thermodynamic equilibrium that may be reached in those DM halos. \add{Interestingly, the mean $\alpha$ value obtained here for Einasto models is roughly $0.4$, implying a pronounced inner-halo density drop (i.e leading to an almost flat inner-slope, see \cref{fig:profile-illustration-mep}), such that the halos look more like the fermionic profiles, indicating instead a possible relevance of an underlying MEP mechanism for halo formation.} Indeed, following the work done in \cite{2021MNRAS.502.4227A} for such fermionic profiles, we have found that typical galaxies belonging to this sub-group (with $W_p \ll 1$) are found to be thermodynamically and dynamically stable, with an outer-halo morphology of polytropic nature (see fig. \ref{fig:halo-profiles}). This may be evidencing a fundamental and deep link between thermodynamics of self-gravitating fermions and galaxy formation and morphology. 

\item[Other Universal relations] We have analyzed in Appendix \ref{sec:parameter-correlations} the Ferrarese relation between the total halo mass and the mass of the supermassive central object. In particular, we have studied the $M_c$-$M_{\rm tot}$ relation --- as first studied in \citet{2019PDU....24..278A} within the fermionic \textit{core-halo} RAR profiles --- for typical dwarf to larger galaxy types and extended here for disk galaxies of the SPARC data set. \add{Interestingly, for the sub-sample of galaxies where the fermionic model provides comparably good fits as Einasto or DC14 models (i.e. with $W_p < 10$)}, the fermionic core-halo solutions predict that the SPARC galaxies have a quantum core mass between $\SI{E4}{\Msun}$ and few $\SI{E6}{\Msun}$ with few reaching masses up to $\SI{E7}{\Msun}$. The total mass spans a range from $\SI{E9}{\Msun}$ to few $\SI{E12}{\Msun}$ as shown in \cref{fig:SPARC:Ferrarese}.

A notable prediction of the above fermionic sub-sample ($W_p < 10$), as compared to the Ferrarese relation \citep{2002ApJ...578...90F}, is that for typical SPARC galaxies having total masses $\sim \SIrange{E9}{E10}{\Msun}$ there seems to be no clear correlation \add{between the core mass $M_c$ and the total DM mass $M_{\rm tot}$ since} solutions show a wide spread in the mass plane (see white dots in \cref{fig:SPARC:Ferrarese}). Even if this result seems to be qualitatively in line with the one found observationally in \cite{2011Natur.469..377K} (i.e. for small enough galaxies with typical circular halo velocities of about \SIrange{50}{150}{\kilo\metre/\second}), it has to be taken with caution since there is much uncertainty (up to about two orders of magnitude) in the core mass $M_c$ per given halo mass (see e.g. middle top panel in \cref{fig:chi-analysis}). Only galaxies with dispersion velocity data down to the central regions allowing to infer the central object mass, can help to better constraint the core-halo solutions.

Polytropic-like solutions of the fermionic model ($W_p \ll 1$) provide a distinct connection between the halo and the core. Even with a lack of data in the central region, such a core-halo connection allows (up to some degree of uncertainty) to constrain the inferred core mass $M_c$. (see e.g. upper panel of \cref{fig:chi-analysis}). \add{The differentiation of the accretion process by a BH or a fermionic
DM core of the baryonic matter which tend to accumulate in the central regions of galaxies is the subject of forthcoming publications.}
%\add{Further insights on the expected phenomenology of baryonic matter (in form of gas and dust) which should tend to accumulate and accrete around the fermionic cores, and how to differentiate with the BH paradigm, are given in Appendix \ref{sec:parameter-corelation:ferrarese}}.

%On the other hand, for the other MEP isothermal-like sub-sample (i.e. with $W_p > 10$), the galaxies follow a better defined correlation in the mass plane  of the form: 

%is a break in the relation at about $\SI{E11}{\Msun}$ and towards the dwarf galaxy end of the correlation, a result which is qualitatively in line 
% Of great interest would be therefore the extension of the relation down to dwarf galaxies what is under current investigation in our group.
%From the analysis of SPARC galaxies we found that spirals have very different halos regarding the cutoff (i.e. $W_p$ in the MEP model). Those different cutoffs correspond to different slopes of the RAR relation in the DM dominated regime. According to the fermionic MEP model we were able to identify a sub-group of SPARC galaxies with a strong cutoff $W_p \lesssim 10$

Finally, the \textit{constancy} of the surface density \citep{2009MNRAS.397.1169D} for SPARC galaxies is also achievable within the fermionic DM model. From the Carnegie-Irvine Galaxy Survey \citep{2011ApJS..197...21H} we have extracted the absolute magnitude for nine overlapping SPARC galaxies. The surface density predictions of that sub-sample are well in agreement with observations.\\ %It is important to emphasize that the majority of predicted surface densities remains within the $3\sigma$ uncertainty as shown in \cref{fig:SPARC:Donato}.
%\subsubsection*{Acceleration correlation}

We thank B. Famey for useful discussions. We thank the anonymous referee who helped to improve the presentation of this work.
\end{description}

%The radial acceleration relation \citep{2016PhRvL.117t1101M} as well as the equivalent mass discrepancy acceleration relation \citep{2004ApJ...609..652M,2014Galax...2..601M} show clearly a link between the acceleration due to the baryonic matter and the acceleration due to dark matter. This relation is 

% cutoff importance


%\subsubsection*{Goodness of fit}
% goodness of model analysis


% relevance of underlying physics


% special attention to oscillations
%Special attention has to be given to galaxies with oscillations in the rotation curve. All considered DM models fail in fitting those rotation curves. This is not surprising, since all competing DM models except MEP have only one maximum in the rotation curve by design. The oscillations in the outer halo tail of the MEP model, which are present only with low particle escape (i.e. $W_p \gtrsim 10$), are too long ranged for a convenient explanation. With an increase in particle escape (i.e. $W_p \lesssim 10$) the halo rotation curve develops a single maximum, similar to the other DM models. Finally, the majority of the galaxy-sample seem to have a lack of information in the very outer halo (e.g. due to faint stars) keeping the behavior in the very low acceleration regime ($\lesssim \SI{E-12}{\metre\per\second^2}$) in secret.



%\subsubsection*{Universal relations}
% core-halo relation (Ferrarese)


% diversity and uncertainty
%We want to note that the thinking of a narrow $M_c$-$M_{\rm tot}$ relation as suggested by \citet{2002ApJ...578...90F} might be misleading according to the predictability analysis of the fermionic MEP model \citep{2018PDU....21...82A,2019PDU....24..278A}. In particular, the model predicts a much higher diversity in the $M_c$-$M_{\rm tot}$ population what is supported by the SPARC results. On the other hand, the diversity is due to some uncertainty in the parameter space (e.g. the halo cutoff parameter $W_p$). Better observations in the inner halo are needed to narrow those uncertainties.

% constant surface density (Donato)



%\subsubsection*{Remarks}
% how to deal with oscillations (information filter)
%We remind to interpret the results from isothermal galaxies, corresponding to $M_{\rm tot} = M_b \ll M_s$, with caution. Compared to the the remaining galaxies they have either a lack of information or short ranged oscillations in the outer halo what prohibits to constrain the cutoff parameter with certainty. The lack of information may be simply solved with future surveys while the oscillations, what may be regarded as an abundance of information, requires further investigations. %A truncation (information filter) shortly after the first maximum in the rotation curve would certainly allow to compare with other galaxies, which provide only one maximum bump at best. We expect that such additional analysis will unveil more profound connections between the dark matter and the morphological type.

% how to deal with oscillations (multi-component?)
%Although, the very different oscillations may be due to ongoing relaxation processes it might be worth to consider also multi-component halo models. It is probable that the fermionic MEP model enhanced with baryonic contributions will help in this analysis and thus to understand galactic structure formation.

% dynamical classification
%Further, \citet{2017MNRAS.469.2539K} introduced a interesting classification of galaxies based on circular velocity curves. Such a classification based on the inferred dark matter rotation curves would be an interesting alternative to the classical morphological classification, which seems to be linked to dark matter profiles.